%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size
\usepackage[colorlinks = true,
linkcolor = blue,
urlcolor  = blue,
citecolor = blue,
anchorcolor = blue
]{hyperref}
\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Shivaraj B H -- Résumé} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> No. 75 Shiva Nilaya Jnana Jyothi nagar,\\ \> 10th main 5th cross,\\ % Address line 1
\> Bangalore - 560056 \\ % Address line 2
{\bf Date of Birth} \> 23$^{rd}$ May 2000 \\ % Date of birth 
{\bf Nationality} \> Indian % Nationality
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Home Phone} \> +91 7411349755 \\ % Home phone
{\bf Mobile Phone} \> +91 7259592595\\ % Mobile phone
{\bf Email} \> \href{mailto:sbh69840@gmail.com}{sbh69840@gmail.com} \\ % Email address
{\bf Skype} \> \href{https://join.skype.com/invite/hdfGrS04mvsL}{live:596832ddabb14976} \\ % Email address

{\bf Github} \> \href{https://github.com/sbh69840}{sbh69840} \\ % Email address
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Objective}
Seeking a competitve research environment to contribute to your orgnaization and also help me get closer to building an artificial brain with a conscience. 


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{2016-2018} \> High school (CBSE) - \href{https://srichaitanya.net/}{Sri Chaitanya PU college, Bangalore} \\[5pt]
\>Percentage - 91.8\% Average\\

}

%------------------------------------------------

\tabbedblock{
\bf{2018-2022} \>  BTech in Computer Technology - \href{https://www.dsu.edu.in/}{Dayananda Sagar University, Bangalore}\\[5pt]
\>First year - 9.3/10 CGPA 
}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Achievements}

\job
{Nov 2018}{}
{IEEE Cloud Computing in Emerging Markets 2018}
{http://2018.ieeeccem.org/}
{3$^{rd}$ place in Student PoC paper presentation. \href{https://drive.google.com/file/d/0B6RJRgHLk-CHS0pHREdmczRJZUxhRmF1Mk1va1oxUjZZbzlj/view?usp=sharing}{certificate}}
{I presented a PoC paper on the topic \href{https://drive.google.com/file/d/1EsZuI-OXfA8jqWlqR0KJepeyxaUbABOe/view?usp=sharing}{Signature recognition and verification using 1D convolution and HOG descriptors.} The conference was scheduled for two days, I had to present the paper on the second day. To make full use of the Day 1: during the project showcase, I asked few spectators to try to forge any signature from the list of trained signatures (To try fooling the algorithm). None of them were able to, I took all the 10 tried forgeries and added it to my presentation to show on Day 2 that none of them were able to forge.}

%------------------------------------------------

\job
{Feb 2017}{}
{Sideicon - (Android app)}
{https://play.google.com/store/apps/details?id=shiv.raj.admin.sideicon}
{1900+ downloads, 39 reviews, 4.5 stars}
{This was my first app, which went live on the play store. I took nearly 6 months to get this app up and running. A fellow YouTuber also featured my app in his \href{https://youtu.be/2xnldqbf5Nc?t=137}{top 10 apps video}. It had over 9000 views. I was 16 years old at that time.}

%----------------------------------------------------------------------------------------
\job
{Jul 2018}{}
{Machine hack - How To Choose The Perfect Beer}
{https://www.machinehack.com/course/how-to-choose-the-perfect-beer/}
{7$^{th}$ place.}
{A hackathon held by Machine hack which was based on predicting the beer score out of 5. My position on leaderboard fluctuated between 1, 2, 3 and at the end of two months I was \href{https://www.machinehack.com/course/how-to-choose-the-perfect-beer/leaderboard}{placed 7$^{th}$.}}

%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Other projects}
\skillgroup{Projects and competitons}
{
	\textit{Web app} - \href{https://github.com/sbh69840/photo-mation}{Photomation} (website)\\
	\textit{Android app} - \href{https://github.com/sbh69840/interview}{Quiz application using dart}\\
	\textit{Ethereum smart contracts} - \href{https://github.com/sbh69840/CompanyBlockchain}{Global blockchain competition}\\
	
}


%------------------------------------------------


%------------------------------------------------


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\interestsgroup{
\interest{Badminton, table tennis, cricket}
}

%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

%\section{Referees}

%\parbox{0.5\textwidth}{ % First block
%\begin{tabbing}
%\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the %block
%{\bf Name} \>  Dr. Chandra Vaidyanathan \\ % Referee name
%{\bf University} \> Dayananda Sagar University \\ % Referee company
%{\bf Position} \> Mathematics HOD \\ % Referee job title 
%{\bf Contact} \> \href{mailto:chandra-math@dsu.edu.in}{chandra-math@dsu.edu.in} % Referee contact information
%\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block

\end{tabbing}}

%----------------------------------------------------------------------------------------

\end{document}